Optimal Fitting of Planar Curves to Prescribed Constraints

### 2014-02-02 idp/documents/documentation/paper.tex
worked on a few TODOs, fixed some issues with floats

% TODO: consider splitting some illustrations into multiple figures if there is still space left at the end
% TODO: expand n't and *'s contractions
% TODO: check if all quotations are done `like this'
% TODO: consistent use of polynomial, planar, plane, parametric, curve

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/examples_bezier.pdf}
					\caption{Bézier Spline Examples (left: Fluttershy \cite{fluttershy}, right: Lugia \cite{lugia})}
					\label{figure:examples_bézier}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/examples_spiro.pdf}
					\caption{Spiro Spline Examples (left: Fluttershy \cite{fluttershy}, right: Lugia \cite{lugia})}
					\label{figure:examples_spiro}
				\end{figure}

@@

			\begin{figure}[htbp]
				\centering
				\includegraphics[width=\textwidth]{content/output/description-based_curves.pdf}
				\caption{Description-Based Curves}
				\label{figure:description-based_curves}
			\end{figure}

@@

				% TODO: explain this in more detail (o--o----------------o, pull last specification, makes wobbly segment at beginning) 
				With this setup, it seems advisable to also include the curve's total arc length in the specification. This way, one can specify curves that don't have any specification items associated to their start and end points. Also, with unspecified curve length, changing any specification item may inadvertently change the curve's total arc length, thus possibly adversely affecting other parts of the curve whose specification item positions are given as a fraction of the curve's total arc length.

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/fairness_mec.pdf}
					\caption{Minimum Energy Curve Examples. Point specification items are represented as red dots, direction specification items are represented as green tangent lines.}
					\label{figure:minimum_energy_curve_examples}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/fairness_mvc.pdf}
					\caption{Minimum Variation Curve Examples. Point specification items are represented as red dots, direction specification items are represented as green tangent lines.}
					\label{figure:minimum_variation_curve_examples}
				\end{figure}

@@

			% TODO: make it clear that splines imply segmentation
			Polynomial curves were chosen since they are mathematically simple, very flexible through the choice of their degree, and well-suited to approximate a variety of smooth curves. We opted to use polynomial splines since they allow approximating more complex curves without involving polynomials of excessively high degree, which are known to have poor stability.

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=100mm]{content/output/linear_segmentation.pdf}
					\caption{Linear Segmentation}
					\label{figure:linear_segmentation}
				\end{figure}

@@

				% TODO: sketch overall curve derivation process similar to the summary slide

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/subsystems.pdf}
					\caption{Subsystem Decomposition of the Kurve Project}
					\label{figure:subsystem_decomposition}
				\end{figure}

@@

			\subsection{Specification}
				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/specification_class_diagram.pdf}
					\caption{Class Diagram of Specification-Related Classes}
					\label{figure:specification_class_diagram}
				\end{figure}

@@

			\subsection{Optimization}
				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/optimization_class_diagram.pdf}
					\caption{Class Diagram of Optimization-Related Classes}
					\label{figure:optimization_class_diagram}
				\end{figure}

@@

		\section{User Interface}
			\subsection{Implementation}
				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/ui_components_class_diagram.pdf}
					\caption{Class Diagram of the User Interface Components}
					\label{figure:ui_components_class_diagram}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/ui_components.pdf}
					\caption{Overview of the User Interface in Kurve}
					\label{figure:ui_components}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/ui_speeds.pdf}
					\caption{Example of a Curve that is `Overspecified' (i.e. the speed of the curve cannot be kept constant due to the high amount of constraints)}
					\label{figure:ui_speeds}
				\end{figure}

@@

			\begin{figure}[htbp]
				\centering
				\includegraphics[width=\textwidth]{content/output/examples_prototype.pdf}
				\caption{Prototype Curve Design Tool Examples (left: Fluttershy \cite{fluttershy})}
				\label{figure:examples_prototype}
			\end{figure}

>>>>

% TODO: expand n't and *'s contractions
% TODO: check if all quotations are done `like this'
% TODO: consistent use of polynomial, planar, plane, parametric, curve

@@

				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{content/output/examples_bezier.pdf}
					\caption{Bézier Spline Examples (left: Fluttershy \cite{fluttershy}, right: Lugia \cite{lugia})}
					\label{figure:examples_bézier}
				\end{figure}

@@

				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{content/output/examples_spiro.pdf}
					\caption{Spiro Spline Examples (left: Fluttershy \cite{fluttershy}, right: Lugia \cite{lugia})}
					\label{figure:examples_spiro}
				\end{figure}

@@

			\begin{figure}[htb]
				\centering
				\includegraphics[width=\textwidth]{content/output/description-based_curves.pdf}
				\caption{Description-Based Curves}
				\label{figure:description-based_curves}
			\end{figure}

@@

				With this setup, it seems advisable to also include the curve's total arc length in the specification. This way, one can specify curves that don't have any specification items associated to their start and end points. Also, with unspecified curve length, changing any specification item may inadvertently change the curve's total arc length, thus possibly adversely affecting other parts of the curve whose specification item positions are given as a fraction of the curve's total arc length. For instance, with three point specification items on the curve, pulling the third one further away from the second will increase the total arc length of the curve, thus also increasing the arc length of the curve segment between the first and the second point specification item, thereby unintentionally creating a bulge between those two specification items.

@@

				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{content/output/fairness_mec.pdf}
					\caption{Minimum Energy Curve Examples. Point specification items are represented as red dots, direction specification items are represented as green tangent lines.}
					\label{figure:minimum_energy_curve_examples}
				\end{figure}

@@

				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{content/output/fairness_mvc.pdf}
					\caption{Minimum Variation Curve Examples. Point specification items are represented as red dots, direction specification items are represented as green tangent lines.}
					\label{figure:minimum_variation_curve_examples}
				\end{figure}

@@

			Polynomial curves were chosen since they are mathematically simple, very flexible through the choice of their degree, and well-suited to approximate a variety of smooth curves. Since polynomials of high degree are known to have poor stability, we opted to use polynomial splines, which allows us to increase the segment count, rather than the degree, in order to approximate more complex curves.

@@

				\begin{figure}[htb]
					\centering
					\includegraphics[width=100mm]{content/output/linear_segmentation.pdf}
					\caption{Linear Segmentation}
					\label{figure:linear_segmentation}
				\end{figure}

@@

				Once the optimization problem is put together, it is passed to the opimization solver, which will return the optimized coefficients of the segment polynomials. These segment polynomials are then assembled according to the layout described in section \ref{section:segmentation_notation} in order to obtain the final curve.

@@

				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{content/output/subsystems.pdf}
					\caption{Subsystem Decomposition of the Kurve Project}
					\label{figure:subsystem_decomposition}
				\end{figure}

@@

			\subsection{Specification}
				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{content/output/specification_class_diagram.pdf}
					\caption{Class Diagram of Specification-Related Classes}
					\label{figure:specification_class_diagram}
				\end{figure}

@@

			\subsection{Optimization}
				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{content/output/optimization_class_diagram.pdf}
					\caption{Class Diagram of Optimization-Related Classes}
					\label{figure:optimization_class_diagram}
				\end{figure}

@@

		\section{User Interface}
			\subsection{Implementation}
				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{content/output/ui_components_class_diagram.pdf}
					\caption{Class Diagram of the User Interface Components}
					\label{figure:ui_components_class_diagram}
				\end{figure}

@@

				% TODO: make this smaller, maybe use landscape format
				\begin{figure}[p]
					\centering
					\includegraphics[width=\textwidth]{content/output/ui_components.pdf}
					\caption{Overview of the User Interface in Kurve}
					\label{figure:ui_components}
				\end{figure}

@@

				% TODO: make this smaller, maybe use landscape format
				\begin{figure}[p]
					\centering
					\includegraphics[width=\textwidth]{content/output/ui_speeds.pdf}
					\caption{Example of a Curve that is `Overspecified' (i.e. the speed of the curve cannot be kept constant due to the high amount of constraints)}
					\label{figure:ui_speeds}
				\end{figure}

@@

			\begin{figure}[htb]
				\centering
				\includegraphics[width=\textwidth]{content/output/examples_prototype.pdf}
				\caption{Prototype Curve Design Tool Examples (left: Fluttershy \cite{fluttershy})}
				\label{figure:examples_prototype}
			\end{figure}
